---
title: "Report"
author: "Dr. Chuck Zumbaugh"
date: "10/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('analysis.R', local = knitr::knit_global())
```
# ASI 561 Nutrient Digestibility in Sheep Analysis Report
## Table of Contents
* [Crude Protein Digestibility](#crude-protein-digestibility)
* [Crude Fat Digestibility](#fat-digestibility)
* [NDF Digestibility](#neutral-detergent-fiber-digestibility)
* [ADF Digestibility](#acid-detergent-fiber-digestibility)
* [OM Digestibillity](#organic-matter-digestibility)

## Crude Protein Digestibility
### Analysis of Variance (transformed)
```{r echo=FALSE}
anovas$asin_cp

```

### Analysis of Variance (untransformed)
```{r echo=FALSE}
untrans_anova$CP_dig
```

### Predicted (least squares) means and pairwise comparisons
```{r echo=FALSE}
response_means$asin_cp
```

### Predicted means (untransformed)
```{r echo=FALSE}
untrans_means$CP_dig
```

### Contrasts
```{r echo=FALSE}
contr_effect$asin_cp
```

### Model Diagnostics
```{r echo=FALSE, message=FALSE}
create_diagnostic_plots(models$asin_cp, "CP")
```

## Fat Digestibility
### Analysis of Variance
```{r echo=FALSE}
anovas$asin_fat

```

### Analysis of Variance (untransformed)
```{r echo=FALSE}
untrans_anova$Fat_dig
```

### Predicted (least squares) means
```{r echo=FALSE}
response_means$asin_fat

```

### Predicted means (untransformed)
```{r echo=FALSE}
untrans_means$Fat_dig
```

### Contrasts
```{r echo=FALSE}
contr_effect$asin_fat
```

### Model Diagnostics
```{r echo=FALSE, message=FALSE}
create_diagnostic_plots(models$asin_fat, "Fat")
```

## Neutral Detergent Fiber Digestibility
### Analysis of Variance (transformed)
```{r echo=FALSE}
anovas$asin_ndf

```

### Analysis of Variance (untransformed)
```{r echo=FALSE}
untrans_anova$NDF_dig
```

### Predicted (least squares) means and pairwise comparisons
```{r echo=FALSE}
response_means$asin_ndf
means$asin_ndf$contrasts

```

### Predicted means (untransformed)
```{r echo=FALSE}
untrans_means$NDF_dig
```

### Contrasts
```{r echo=FALSE}
contr_effect$asin_ndf
```

### Model Diagnostics
```{r echo=FALSE, message=FALSE}
create_diagnostic_plots(models$asin_ndf, "NDF")
```

## Acid Detergent Fiber Digestibility
### Analysis of Variance (transformed)
```{r echo=FALSE}
anovas$asin_adf
```

### Analysis of Variance (untransformed)
```{r echo=FALSE}
untrans_anova$ADF_dig
```

### Predicted (least squares) means
```{r echo=FALSE}
response_means$asin_adf
```

### Predicted means (untransformed)
```{r echo=FALSE}
untrans_means$ADF_dig
```

### Contrasts
```{r echo=FALSE}
contr_effect$asin_adf
```

### Model Diagnostics
```{r echo=FALSE, message=FALSE}
create_diagnostic_plots(models$asin_adf, "ADF")
```

## Organic Matter Digestibility
### Analysis of Variance (transformed)
```{r echo=FALSE}
anovas$asin_om
```

### Analysis of Variance (untransformed)
```{r echo=FALSE}
untrans_anova$OM_dig
```

### Predicted (least squares) means
```{r echo=FALSE}
response_means$asin_om

```

### Predicted means (untransformed)
```{r echo=FALSE}
untrans_means$OM_dig
```

### Contrasts
```{r echo=FALSE}
contr_effect$asin_om
```

### Model Diagnostics
```{r echo=FALSE, message=FALSE}
create_diagnostic_plots(models$asin_om, "OM")
```
